### 2018-07-03 pilot_manuscript.Rmd
small updates with mumin

```{r load_packages, include = FALSE}
library("papaja")
```
# Introduction
Talk about MFT, MFQ, MFD
Talk about political discourse, nature of news media in 2018/Trump era
This project brings the two together in holy matrimony.
# Method

@@

####predictor model####
model3 = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
             data = long_mlm, 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|partno)
summary(model3)
anova(model1, model2, model3)

>>>>

```{r load_packages, include = FALSE}
library("papaja")
library(MuMIn)
```
# Introduction
Talk about MFT, MFQ, MFD
Talk about political discourse, nature of news media in 2018/Trump era
This project brings the two together in holy matrimony.
# Method

@@

####predictor model####
model3 = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
             data = long_mlm, 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|partno)
summary(model3)
anova(model1, model2, model3)
r.squaredGLMM(model3) #gives you two, report both
